---
title: "How stressed are TN front line workers?"
output: 
  html_document:
    css: /home/arunkumar/Documents/GitHub/aruncps.github.io/assets/css/main.css
    includes:
       in_header: GA_Script.html
---
* **Source:** [TN COVID Beds](https://tncovidbeds.tnega.org/)
* **Latest data import date:** `r format(Sys.time(), '%d %B, %Y')`
* **Summary:** Tamil Nadu Government publishes COVID bed availability of **"Normal, O2 & ICU Beds"**, by each district. Using it, heatmap is generated to view **"The STRESSLEVEL of frontline workers"**, by District and Area.


## List of Districts: {#lod}
  + [All District](#AllDistrict)
  + [Ariyalur](#Ariyalur)
  + [Chengalpattu](#Chengalpattu)
  + [Chennai](#Chennai)
  + [Coimbatore](#Coimbatore)
  + [Namakkal](#Namakkal)
  
  
```{r packages, results="hide",echo=FALSE, message=FALSE, warning=FALSE}
# IMPORT Packages 
lapply(c("tidyverse","rvest","stringr","hrbrthemes","viridis","plotly","scales","fs","RSelenium","stringr","zoo","tidyquant"), library, character.only = TRUE)

#------- Import CSV
file_TN_CovidBeds<-paste0("/home/arunkumar/Documents/GitHub/TN_Beds/TN_CovidBeds.csv")
file_byDist_CovidBeds<-paste0("/home/arunkumar/Documents/GitHub/TN_Beds/byDist_CovidBeds.csv")

# Verify No. of beds before writing to csv
TN_CovidBeds<-read.table(file_TN_CovidBeds,header=TRUE, row.names=NULL)
TN_CovidBeds<-tibble(TN_CovidBeds)
# TN_CovidBeds %>% group_by(importDate) %>% summarise(n(),sum(All_Bed_Total)) %>% arrange(desc(importDate))

# Verify No. of hospitals before writing to csv
byDist_CovidBeds<-read.table(file_byDist_CovidBeds,header=TRUE, row.names=NULL)
byDist_CovidBeds<-tibble(byDist_CovidBeds)
# byDist_CovidBeds %>% group_by(importDate) %>% summarise(n(),sum(All_Bed_Total)) %>% arrange(desc(importDate))

Dist_Beds <- byDist_CovidBeds %>% 
                group_by(importDate, District) %>%
                summarize(
                  No_of_Hospitals=sum(No_of_Hospitals),
                  Normal_Bed_Occupancy=sum(Normal_Bed_Occupancy),
                  O2_Bed_Occupancy=sum(O2_Bed_Occupancy),
                  ICU_Bed_Occupancy=sum(ICU_Bed_Occupancy),
                  All_Bed_Occupancy=sum(All_Bed_Occupancy)
                ) %>%
                select(importDate, District, No_of_Hospitals, Normal_Bed_Occupancy, O2_Bed_Occupancy, ICU_Bed_Occupancy, All_Bed_Occupancy ) %>%
                ungroup()

Dist_Beds$importDate<-as.Date(as.character(Dist_Beds$importDate))

Dist_Beds$Normal_Bed_Occupancy_Y1<-cut(Dist_Beds$Normal_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)
Dist_Beds$O2_Bed_Occupancy_Y1<-cut(Dist_Beds$O2_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)
Dist_Beds$ICU_Bed_Occupancy_Y1<-cut(Dist_Beds$ICU_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)
Dist_Beds$All_Bed_Occupancy_Y1<-cut(Dist_Beds$All_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)

# ----------------------------------
# District split into Area
# ----------------------------------
file_AreaSplit_TN_CovidHospitals<-paste0("/home/arunkumar/Documents/GitHub/TN_Beds/AreaSplit_TN_CovidHospitals.csv")
AreaSplit_TN_CovidHospitals<-read.csv(file_AreaSplit_TN_CovidHospitals,header=TRUE, row.names=NULL)
AreaSplit_TN_CovidHospitals<-tibble(AreaSplit_TN_CovidHospitals)

tbl_TN_Area_CovidBeds <- TN_CovidBeds %>% mutate(HospitalName=str_trim(HospitalName)) %>%
  inner_join(AreaSplit_TN_CovidHospitals %>% mutate(HospitalName=str_trim(HospitalName)), by = c("District"="District","HospitalName"="HospitalName"))
  
TN_Area_CovidBeds <- tbl_TN_Area_CovidBeds %>% 
  group_by(importDate,District,Area) %>% 
  summarize(
    No_of_Hospitals=length(HospitalName),
    Normal_Bed_Vacant=sum(Normal_Bed_Vacant),Normal_Bed_Total=sum(Normal_Bed_Total),
    O2_Bed_Vacant=sum(O2_Bed_Vacant),O2_Bed_Total=sum(O2_Bed_Total),
    ICU_Bed_Vacant=sum(ICU_Bed_Vacant),ICU_Bed_Total=sum(ICU_Bed_Total),
    All_Bed_Vacant=sum(All_Bed_Vacant),All_Bed_Total=sum(All_Bed_Total)
  ) %>% 
  mutate(
    Normal_Bed_Occupancy=(Normal_Bed_Total-Normal_Bed_Vacant)/Normal_Bed_Total,
    O2_Bed_Occupancy=(O2_Bed_Total-O2_Bed_Vacant)/O2_Bed_Total,
    ICU_Bed_Occupancy=(ICU_Bed_Total-ICU_Bed_Vacant)/ICU_Bed_Total,
    All_Bed_Occupancy=(All_Bed_Total-All_Bed_Vacant)/All_Bed_Total
  ) %>% 
  select(importDate, District, Area, No_of_Hospitals, Normal_Bed_Occupancy, O2_Bed_Occupancy, ICU_Bed_Occupancy, All_Bed_Occupancy ) %>%
  ungroup()

TN_Area_CovidBeds$importDate<-as.Date(as.character(TN_Area_CovidBeds$importDate))

TN_Area_CovidBeds$Normal_Bed_Occupancy_Y1<-cut(TN_Area_CovidBeds$Normal_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)
TN_Area_CovidBeds$O2_Bed_Occupancy_Y1<-cut(TN_Area_CovidBeds$O2_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)
TN_Area_CovidBeds$ICU_Bed_Occupancy_Y1<-cut(TN_Area_CovidBeds$ICU_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)
TN_Area_CovidBeds$All_Bed_Occupancy_Y1<-cut(TN_Area_CovidBeds$All_Bed_Occupancy,breaks = c(0,0.2,0.4,0.6,0.8,1,Inf),right = FALSE)


```


## All Districts {#AllDistrict}
```{r echo=FALSE, warning=FALSE, fig.height=8, fig.width=7}
ggplot(Dist_Beds
       ,aes(importDate, District)) + 
  geom_tile(aes(fill= Normal_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "Normal Bed Occupancy (%)") +
  ylab(label = "District") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Dist_Beds$District) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=8, fig.width=7}
ggplot(Dist_Beds
       ,aes(importDate, District)) + 
  geom_tile(aes(fill= O2_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "O2 Bed Occupancy (%)") +
  ylab(label = "District") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Dist_Beds$District) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=8, fig.width=7}
ggplot(Dist_Beds
       ,aes(importDate, District)) + 
  geom_tile(aes(fill= ICU_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "ICU Bed Occupancy (%)") +
  ylab(label = "District") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Dist_Beds$District) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

###### [Back to full list of Districts](#lod) {style="float:right"}

## Ariyalur {#Ariyalur}

```{r echo=FALSE, warning=FALSE, fig.height=3.5, fig.width=7}
Ariyalur_Area_CovidBeds <- TN_Area_CovidBeds %>% filter(District == "Ariyalur")
ggplot(Ariyalur_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= Normal_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "Normal Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Ariyalur_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=3.5, fig.width=7}
ggplot(Ariyalur_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= O2_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "O2 Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Ariyalur_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=3.5, fig.width=7}
ggplot(Ariyalur_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= ICU_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "ICU Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Ariyalur_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

###### [Back to full list of Districts](#lod) {style="float:right"}

## Chengalpattu {#Chengalpattu}

```{r echo=FALSE, warning=FALSE, fig.height=10, fig.width=7}
Chengalpattu_Area_CovidBeds <- TN_Area_CovidBeds %>% filter(District == "Chengalpattu")

ggplot(Chengalpattu_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= Normal_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "Normal Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Chengalpattu_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=10, fig.width=7}
ggplot(Chengalpattu_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= O2_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "O2 Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Chengalpattu_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=10, fig.width=7}
ggplot(Chengalpattu_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= ICU_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "ICU Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Chengalpattu_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

###### [Back to full list of Districts](#lod) {style="float:right"}

## Chennai {#Chennai}

```{r echo=FALSE, warning=FALSE, fig.height=18, fig.width=7}
Chennai_Area_CovidBeds <- TN_Area_CovidBeds %>% filter(District == "Chennai")

ggplot(Chennai_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= Normal_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "Normal Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Chennai_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=18, fig.width=7}
ggplot(Chennai_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= O2_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "O2 Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Chennai_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=18, fig.width=7}
ggplot(Chennai_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= ICU_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "ICU Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Chennai_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

###### [Back to full list of Districts](#lod) {style="float:right"}

## Coimbatore {#Coimbatore}

```{r echo=FALSE, warning=FALSE, fig.height=14, fig.width=7}
Coimbatore_Area_CovidBeds <- TN_Area_CovidBeds %>% filter(District == "Coimbatore")

ggplot(Coimbatore_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= Normal_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "Normal Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Coimbatore_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=14, fig.width=7}
ggplot(Coimbatore_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= O2_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "O2 Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Coimbatore_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=14, fig.width=7}
ggplot(Coimbatore_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= ICU_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "ICU Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Coimbatore_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

###### [Back to full list of Districts](#lod) {style="float:right"}


## Namakkal {#Namakkal}

```{r echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
Namakkal_Area_CovidBeds <- TN_Area_CovidBeds %>% filter(District == "Namakkal")

ggplot(Namakkal_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= Normal_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "Normal Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Namakkal_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
ggplot(Namakkal_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= O2_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "O2 Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Namakkal_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

```{r echo=FALSE, warning=FALSE, fig.height=7, fig.width=7}
ggplot(Namakkal_Area_CovidBeds
       ,aes(importDate, Area)) + 
  geom_tile(aes(fill= ICU_Bed_Occupancy_Y1),colour="white",size=0.25) +
  # scale_fill_gradient(low="#fffaaf", high="#ff4747") +
  scale_fill_manual(breaks=c("[0,0)", "[0,0.2)", "[0.2,0.4)", "[0.4,0.6)", "[0.6,0.8)", "[0.8,1)","[1,Inf)"),
                    values = c("#e6e6e6", "#c9ff96", "#fffa96","#ffc800", "#ff7d00", "#ff0000","#af0000"),
                    labels = c("0", "0-20", "20-40", "40-60", "60-80", "80-100","100" ),
                    name = "ICU Bed Occupancy (%)") +
  ylab(label = "Area") +
  xlab(label = "Date") +
  scale_y_discrete(limits = rev(levels(as.factor(droplevels(Namakkal_Area_CovidBeds$Area) ))) 
                   ,position = "left") +
  theme_classic() +
  theme(strip.placement = "outside",
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(), # Remove y-axis title
        strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        legend.position="top"
  ) +
  scale_x_date(date_breaks = "1 week", date_minor_breaks = "1 day", date_labels = "%d/%m")

```

###### [Back to full list of Districts](#lod) {style="float:right"}